Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
Fixes LaTeX errors in appendix
Remove '(RGB)' from abstract.

\begin{abstract}
%%%
When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a dense stellar wind.
Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.  
The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with the Square Kilometer Array. 
\end{abstract}

@@

An objection to the above estimate is that the singularity in the $E_{\rm recoil} \rightarrow 0$ limit arises from the long range nature of Coulomb interaction which of course is absent in the real problem.
Far away, the ionizing electron sees the dipole moment of the neutral atom.
However, for energy transfer of order a Rydberg $\alpha/2a_0$ we can estimate the transfer momentum and see that it is larger than the inverse of the Bohr radius $a_0$.
This implies that in this range the above estimate may actually be reliable. The transfer momentum is
\begin{equation}
q^2 =\frac{1}{4} m^2 \vrel^2 (\sin^2\theta +(1-\cos \theta)^2)= m^2\vrel^2 \sin^2 \frac{\theta}{2}.
\end{equation}
Comparison with (\ref{eq:Erec}) shows
\begin{equation}
E_{\rm recoil} = \frac{q^2}{2m}.
\ee
Now set $E_{\rm recoil} \sim \alpha/a_0$ to get
\be
q \sim \sqrt{\frac{m\alpha}{a_0}}\sim \frac{1}{a_0}
\ee
where we used $a_0 = 1/\alpha m$.

>>>>

\begin{abstract}
%%%
When planet-hosting stars evolve off the main sequence and go through the red-giant branch, the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a dense stellar wind.
Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.  
The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with the Square Kilometer Array. 
\end{abstract}

@@

An objection to the above estimate is that the singularity in the $E_{\rm recoil} \rightarrow 0$ limit arises from the long range nature of Coulomb interaction which of course is absent in the real problem.
Far away, the ionizing electron sees the dipole moment of the neutral atom.
However, for energy transfer of order a Rydberg $\alpha/2a_0$ we can estimate the transfer momentum and see that it is larger than the inverse of the Bohr radius $a_0$.
This implies that in this range the above estimate may actually be reliable. The transfer momentum is
\begin{equation}
q^2 =\frac{1}{4} m^2 v_{\rm rel}^2 (\sin^2\theta +(1-\cos \theta)^2)= m^2v_{\rm rel}^2 \sin^2 \frac{\theta}{2}.
\end{equation}
Comparison with (\ref{eq:Erec}) shows
\begin{equation}
E_{\rm recoil} = \frac{q^2}{2m}.
\end{equation}
Now set $E_{\rm recoil} \sim \alpha/a_0$ to get
\begin{equation}
q \sim \sqrt{\frac{m\alpha}{a_0}}\sim \frac{1}{a_0}
\end{equation}
where we used $a_0 = 1/\alpha m$.
